We need to beat namespotting, no idea how

### 2023-01-26 paperSubmission/paperSubmission1.tex
some additions

To maximize the potential impact of our interventions and to minimize  accidental instigation of more verbal aggression, we decided to educate the volunteers on scientifically grounded strategies for normative influence and persuasive messaging.  Let us elaborate.
 Social norms are agreed to be powerful determinants of human behavior. 
According to theories of norm compliance people tend to comply with the norms they are exposed to \citep{morris2018common}, \citep{cialdini1990focus}.  A good deal of studies have found that perceptions of what others are doing causes us to behave similarly. Norms can be applied to exert persuasive impact, for example to solve a social problem such as littering or wasting resources \citep{cialdini2006managing, cialdini1990focus, goldstein2008room}.

@@

Some scholars propose that perceived social norms serve as shortcuts helping us quickly adapt to new environments \citep{cialdini1990focus}. Others say that we are only motivated by norms we have internalized during socialization, so the normative influence can only be exerted if the norm resonates with our internal value system \citep{morris2018common}.  Focus Theory of Normative Conduct \citep{kallgren2000focus} is a psychological, theoretical framework used for understanding best conditions and practices for exerting normative influence. Its main assumption is that norms that are focal in attention are likely to influence behavior.  %explain on an example cialdini experiment
To achieve persuasive impact a distinction between two types of norms has to be made. While it might sound strange to talk about desriptive norms, this is the way the terminology in the field developed, so we will keep using such terms.  A descriptive norm refers to what is typically done, by showing  examples of  normal behavior in a given situation, and injunctive or prescriptive norm refers to what is commonly approved, such the rules of proper conduct and moral beliefs \citep{cialdini1990focus}.  A descriptive norm motivates compliance by providing evidence about what is likely to be an effective and adaptive action, while injuctive norm motivates by informing which actions will be approved and which will result in social sanctions \citep{yanowitzky2006communication, cialdini2004social, kallgren2000focus}.

@@

The positive influence of injunctive and descriptive norms on unwanted social behavior was first presented in a study on littering in public spaces conducted by \citet{cialdini1990focus}. Study subjects were exposed to either descriptive or injunctive anti-littering norm, and the impact on the littering behavior was observed. In the descriptive condition the subjects were exposed to a clean or littered environment, serving as a proof of choices made by others. In the injunctive condition participants received messages stating the anti-littering norm.

Injunctive messages directly asking not to litter had significantly reduced littering, and subjects littered more in a highly littered environment, and littered less in a clean environment although these effects were not statistically significant. %which ones 
Although seeing litter in an otherwise clean environment could have also engaged an injunctive norm, as it might have reminded subjects about societal objections to littering.

@@

A descriptive norm can be also evoked by providing a written information about what others usually do. \citet{goldstein2008room} distributed flyers with normative messages that contained descriptive information about reuse of hotel towels (“the majority of guests reuse their towels”). This strategy has been proven superior to traditional appeals focusing on environmental protection. Moreover, normative appeals were most effective when the described behavior occurred in the same location (“in this hotel  room”), and so referred to the so-called local norms.

@@

%On the other hand, when it comes to pro-environmental choices, people are more likely to conform to information about what others don't do rather than what others do, building on an evolutionary predisposition to more urgently attend to negative rather than positive stimuli @bergquist2019and.  
%Stosujemy normatywne i empatyczne interwencje - w literaturze te mechanizmy psychologiczne są opisane jako skuteczne w obniżaniu agresji - cytujemy literature. 
%W jakich innych badaniach counter speech wykorzystywali empatie i norme - nas (Bilewicz study), Munger, Roma racist, itp..+opisać jak nasze obecne badanie sie rozni - po raz pierwszy wykorztstyujemy collective intelligence ludzie + AI
%describe hypothesis i give argument behind the hypothesis

 In line with this discussion, for the purpose of our study we have distinguished two types of counter responses to personal attacks: ``empathetic'' and ``normative''. The empathetic approach is aimed at countering the so-called desensitization to violence. It is a very dangerous process, finally leading to dehumanization of stigmatized groups. %Unfortunately, the impersonal structure of online space makes it very easy for the desensitization to occur. 
 Being frequently exposed to online hate speech builds tolerance to the phenomenon and as a result we no longer see such statements as offensive, which lowers our sympathy for the victims and increases prejudice. By sending empathetic interventions we hoped to evoke compassion, self-reflection and humanize the person on the other side of the screen \citep{bilewicz2021artificial}.  The normative approach

%To put it in an example, there is a general rule that we should not litter in public spaces (injunctive norm), but we are much more likely to leave our garbage, when there’s evidence that other people did not follow the rule - the space is littered with trash (descriptive norm). We hope that our interventions will provide constructive social cues about acceptable forms of communication and influence the way users converse in a given community.

%Another phenomenon illustrating the power of the context is the bystander effect. The bystander theory  states that individuals are less likely to offer help to a victim when there are other people present - the greater the number of bystanders, the less likely it is that one of them will help. But it takes only one helpful volunteer for others to follow. The study by Machackova and others (2015) have shown the bystander effect also takes place online. and a more recent study has shown that ordinary people, with no habit of trolling, will engage in trolling behavior under proper circumstances.

\todo{To sie nie klei ta koncowka, trzeba cos zmienic}

@@

>>>>

To maximize the potential impact of our interventions and to minimize  accidental instigation of more verbal aggression, we decided to educate the volunteers on scientifically grounded strategies for normative influence and persuasive messaging.  Let us elaborate.

ocial norms are agreed to be powerful determinants of human behavior. 
According to theories of norm compliance people tend to comply with the norms they are exposed to \citep{morris2018common, cialdini1990focus}.

Multiple studies have found that perceptions of what others are doing cause us to behave similarly. Norms can be applied to exert persuasive impact, for example, to solve a social problem such as littering or wasting resources \citep{cialdini2006managing, cialdini1990focus, goldstein2008room}.

@@

Some scholars propose that perceived social norms serve as shortcuts helping us quickly adapt to new environments \citep{cialdini1990focus}. Others say that we are only motivated by norms we have internalized during socialization, so the normative influence can only be exerted if the norm resonates with our internal value system \citep{morris2018common}.  %cytowania

The Focus Theory of Normative Conduct \citep{kallgren2000focus} is a  theoretical psychological  framework used for understanding best conditions and practices for exerting normative influence. Its main assumption is that norms that are focal in attention are likely to influence behavior. One important distinction made within this approach is between two types of norms: a descriptive norm refers to what is typically done, by showing an example of normal behavior in a given situation, and an injunctive or prescriptive norm refers to what is commonly approved, such as the rules of proper conduct and moral beliefs \citep{cialdini1990focus}.

A descriptive norm motivates compliance by providing evidence about what is likely to be an effective and adaptive action, while an injunctive norm motivates by informing the agent which actions will be approved and which will result in social sanctions \citep{yanowitzky2006communication, cialdini2004social, kallgren2000focus}.

@@

The positive influence of injunctive and descriptive norms on unwanted social behavior was first presented in a study on littering in public spaces conducted by \citet{cialdini1990focus}. The study subjects were exposed to either descriptive or injunctive anti-littering norms, and the impact on the littering behavior was observed. In the descriptive condition, the subjects were exposed to a clean or littered environment, serving as proof of choices made by others. In the injunctive condition, the participants received messages stating the anti-littering norm.

Injunctive messages directly asking not to litter had significantly reduced littering. The subjects littered more in a highly littered environment and littered less in a clean environment, although these effects were not statistically significant.\footnote{It is also worth noticing that  seeing litter in an otherwise clean environment could have also engaged an injunctive norm, as it might have reminded subjects about societal objections to littering.}

@@

A descriptive norm can be also evoked by providing written information about what others usually do. \citet{goldstein2008room} distributed flyers with normative messages that contained descriptive information about reuse of hotel towels (“the majority of guests reuse their towels”). This strategy has been proven superior to traditional appeals focusing on environmental protection. Moreover, normative appeals were most effective when the described behavior occurred in the same location (“in this hotel  room”), and so referred to, so called, local norms.

@@

In line with the above discussion, for the purpose of this study we have distinguished two types of responses to personal attacks: "empathetic" and "normative". The empathetic approach is aimed at countering the so-called desensitization to violence. It is a very dangerous process, finally leading to the dehumanization of stigmatized groups.  
 Being frequently exposed to online hate speech builds tolerance to the phenomenon and as a result, we no longer see such statements as offensive, which lowers our sympathy for the victims and increases prejudice. By sending empathetic interventions we hoped to evoke compassion and self-reflection, and  to humanize the person on the other side of the screen \citep{bilewicz2021artificial}.

The normative approach stems from the  already discussed psychological research of normative social influence, stating that in ambiguous situations, people tend to rely on social cues, to determine what kinds of behaviors will be accepted. Taking from these studies, we refer to two types of norms: injunctive norms---describing what the members of this community are supposed to do and what is approved or disapproved by others (laws, rules, code of conduct, savoir-vivre, etc.) and descriptive norms---what the members of this community actually do \citep{cialdini_focus_1991, cialdini2004social, cialdini2006managing}.

@@

\section{Managing volunteers}\label{volunteers}

For two months of the treatment period, interventions were conducted by 19 volunteers, recruited  online on an ongoing basis. The call for volunteers was promoted on social media channels, and groups related to volunteering and sent out to 30+ NGOs and organizations with social impact, 10 out of which shared it via their social networks or distributed it among their employees and partners. 
%(Tolerado, CEJI (A Jewish Contribution to an Inclusive Europe), INACH (International Network Against Cyberhate), Humanity in Action Poland, Gdansk Business Week among others).

We expected that each volunteer would conduct around 10 interventions a day. Unfortunately, only a few people got engaged to such an extent at the beginning. Thus, we have implemented various incentives and gamification to increase volunteer engagement. Those included leaderboards, motivational statistics, and week-long contests with a prize. As you can see in Fig \ref{fig:volunteersBasic}, the drop in volunteer engagement is noticeable within the first 2 weeks from the beginning of the treatment period. The introduction of the first competition with an economic incentive (Amazon Gift Card for the most active volunteers) increased the engagement only temporarily. It then dropped dramatically outside of the contest. This forced us to keep repeating contests regularly until the end of the treatment period. Obviously, this is not an optimal and sustainable long-term strategy.

Figure 15 \ref{fig:volunteersModel}  visualizes the result of a Bayesian model of volunteer engagement based on the resulting observational data, with daily baselines and multipliers for enthusiasm and impact of competitions. Four distinct groups emerge from this picture. Those, who are active, and even  more  so during competitions. Those who are evenly active throughout the treatment period. Those, who are active only during competitions, and volunteers whose initial enthusiasm died completely very soon. The multiplier of the volunteer engagement during the competition is only 1.31 which means that their engagement increases by around 30\% during that time. But the enthusiasm of  some of the volunteers had  its drop multiplier even below .9 \textbf{per day of experiment}. It accumulates as time progresses, which means that competitions might not be  effective in volunteer activity resuscitation, especially in the long run.

If we were to conduct a similar experiment with volunteers again, we would test  non-economic motivational schemes---for instance, creating an obligation by signing an agreement with volunteers on conducting at least 10 interventions daily, or creating more engaging content and training during the treatment period.

Besides the issue connected to  low volunteer engagement, we have experienced cases in which people reported negative effects of interventions or even started to get aggressive while responding to attackers. Although we've taken extra measures to support volunteers (a psychologist available to all participants,  and distribution of and guide to their well-being), this aspect cannot be eliminated completely.

Additionally, many volunteers started to intervene in a repetitive manner, which resulted in accusations of behaving like an automated account (bot). During the process, we prepared an additional guide for our volunteers "How to write Powerful Interventions" and rewarded creativity during the contests. Both led to a noticeable increase in creativity, especially when it comes to the most engaged volunteers.

We need to mention at this point that in this experiment, the negative side of the collective intelligence approach outweighs the positive one. In our future endeavors, we will be further exploring the opportunity to employ bots to conduct counter-speech. Even though AI is not endowed with empathy, it can be a powerful ally in evoking empathetic responses and maintaining civil behavior online. An ally, who under the condition of being precise enough to act autonomously, can take the burden off of the shoulders of moderators and the community, not requiring them to  screen through a multitude of potentially aggressive comments.

Another scenario worth considering is a collective intelligence approach in which 90\% of interventions are conducted by an AI while 10\% of the most difficult cases are taken care of by humans, trained professionals, such as moderators. During the study, we had one extraordinary volunteer who was engaged and creative to such an extent that no machine could compete. Collaborating with people like them would considerably optimize the process. Such a trained, engaged, and resilient person could supervise the interventions run by AI and deal with  extreme cases.
